Resilience and Home-Space for WSTS \thanks{This work was partly done while the authors were supported by the Agence Nationale de la Recherche grant BraVAS (ANR-17-CE40-0028).}

### 2023-10-30 VMCAI-revised-version/final.tex
up

Indeed, the structural existential halting problem consists in deciding if 
a system %terminates
have a \alain{un ou tous les run ?}terminating (i.e. finite) run
 from every initial state.

>>>>

Indeed, the structural existential halting problem consists in deciding if 
a system %terminates
have %a \alain{un ou tous les run ?}
at least one terminating (i.e. finite) run
 from every initial state.
